HLPSC: Building and using a seed corpus for the Human Language Project

### 2014-03-20 docs/computEL/data.tex
new heatmap file, added to data.tex

According to Ethnologue, there are 7105 living languages, and 147 living language families. Across all our data sources, we manage to cover 1347 languages in 106 families, which represents 19.0\% of the world's languages. To get a better idea of the kinds of languages represented, we give a breakdown according to their EGIDS scores (Expanded Graded Intergenerational Disruption Scale) in figure \textcolor{blue}{[insert reference here when it's ready]}. The values in each cell have been colored according to proportion of languages represented, with green indicated good coverage and red poor. It's interesting to note that vigorous languages (6a) are poorly represented across all data sources, and worse than more endangered categories. In terms of language documentation, vigorous languages are less urgent goals than those in categories 6b and up, but this highlights an unexpected gap in linguistic resources.

@@

\begin{table}[h!]
\centering
    \begin{tabular}{l|rr|rr}
    ~         				& \#Languages & \#Families 	&\#tokens		& Size	\\ \hline
    ODIN      				& 1,217      & 101       		& 58,556		& 39 MB		\\
    Omniglot  				& 134        & 21        		&	6,749			& 677 KB	\\
    UDHR      				& 355        & 47        		&	33,117		& 5.2 MB	\\
    Wikipedia 				& 209        & 22       		&						& 37 GB		\\ \hline
    \textbf{Combined}	& 1,347			 & 106 
    \end{tabular}
\caption{Corpus Coverage}
\label{table:corpus}
\end{table}

\textcolor{blue}{[insert heatmap here]}

>>>>

According to Ethnologue, there are 7105 living languages, and 147 living language families. Across all our data sources, we manage to cover 1347 languages in 106 families, which represents 19.0\% of the world's languages. To get a better idea of the kinds of languages represented, we give a breakdown according to their EGIDS scores (Expanded Graded Intergenerational Disruption Scale) in figure \ref{fig:heatmap}. The values in each cell have been colored according to proportion of languages represented, with green indicated good coverage and red poor. It's interesting to note that vigorous languages (6a) are poorly represented across all data sources, and worse than more endangered categories. In terms of language documentation, vigorous languages are less urgent goals than those in categories 6b and up, but this highlights an unexpected gap in linguistic resources.

@@

\begin{table}[h!]
\small
\centering
    \begin{tabular}{l|rr|rr}
    ~         				& \#Languages & \#Families 	&\#tokens		& Size	\\ \hline
    ODIN      				& 1,217      & 101       		& 58,556		& 39 MB		\\
    Omniglot  				& 134        & 21        		&	6,749			& 677 KB	\\
    UDHR      				& 355        & 47        		&	33,117		& 5.2 MB	\\
    Wikipedia 				& 209        & 22       		&						& 37 GB		\\ \hline
    \textbf{Combined}	& 1,347			 & 106 
    \end{tabular}
\caption{Corpus Coverage}
\label{table:corpus}
\end{table}

\begin{figure*}[t]
\begin{centering}
\includegraphics[scale=0.6]{heatmap-numbers.png}

\caption{Heatmap of languages in HLPSC according to endangerment status}\label{fig:heatmap}
\end{centering}
\end{figure*}
